Icicle: write once, run once

### 2016-05-21 2016fhpc/section/01-Introduction.tex
ok

The contributions of this paper are:
\begin{itemize}
\item
we describe restrictions on Icicle which guarantee any two queries on the same table can be fused together\sref{s:IcicleSource};
\item
we show an intermediate fold-based language, which makes fusion a simple matter of appending two programs\sref{s:IcicleCore};
\item
and we present benchmarks of our generated code, which compares favourably against standard unix utilities and outperforms our existing system by orders of magnitude\sref{s:Benchmarks}.
\end{itemize}

>>>>

The contributions of this paper are:
\begin{itemize}
\item
we show a simple typesystem that guarantees any two queries on the same table can be fused together, as well as allowing queries to be resumed as new data is received\sref{s:IcicleSource};

\item
we show an intermediate fold-based language, which makes fusion a simple matter of appending two programs\sref{s:IcicleCore};

\item
and we present benchmarks of our generated code, which compares favourably against standard unix utilities and outperforms our existing system by orders of magnitude\sref{s:Benchmarks}.
\end{itemize}
